*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-27 Code/Manuscript_O2.Rmd
Changed table header alignment to remove tabs in header when knitted but it did not work

# This is S1_Table.csv
readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
  select(EnzymeName, EC, KO) %>% 
  knitr::kable(.,
             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
            col.names =  c(
                          "Enzyme Name",
                          "EC",
                          "Kegg Orthology")
             )

@@

# This is S2_Table
knitr::kable(MaxGrowthTable,
             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each strain under each [O~2~], with the corresponding photoperiod, PAR level and spectral waveband.",
            col.names =  c("Strain",
                           "[O~2~] (µM)",
                           "µ~max~ (d^-1^)",
                          "Photoperiod (h)",
                          "PAR (µmol photons m^-2^ s^-1^)",
                          "Spectral waveband (nm)"),
              align = "lccccc"
             )

>>>>

# This is S1_Table.csv
readRDS(file.path(DataIn,"ProchlorococcusEnzymeTable.Rds")) %>% 
  select(EnzymeName, EC, KO) %>% 
  knitr::kable(.,
             caption = "Enzymes shown in Figures \\@ref(fig:ProchlorococcusEnzymeKms),  \\@ref(fig:DNARepairFig) and \\@ref(fig:ProchlorococcusLightEnzymes) with their Enzyme Commission numbers (EC) and Kegg Orthology (KO).",
            col.names =  c(
                          "Enzyme Name",
                          "EC",
                          "Kegg Orthology"),
            align = "lll"
             )

@@

# This is S2_Table
knitr::kable(MaxGrowthTable,
             caption = "The maximum growth rate, µ~max~ (d^-1^) achieved for each strain under each [O~2~], with the corresponding photoperiod, PAR level and spectral waveband.",
            col.names =  c("Strain",
                           "[O~2~] (µM)",
                           "µ~max~ (d^-1^)",
                          "Photoperiod (h)",
                          "PAR (µmol photons m^-2^ s^-1^)",
                          "Spectral waveband (nm)"),
              align = "llllll"
             )
